---
title: "Topographic Maps from .Raw Heightmap Files"
output: html_document
---

This file pulls in .raw files exported from Unity Terrains and turns them into a topographic map with filled contour lines. 

In order to export all of the .raw files from your terrains, we have created a tool called "Export All Terrain Maps." This tool is located in Assets/Editor; the script is called TerrainHeightmapExporter.cs

To use it, load your scene then go to tools > Export All Terrain Maps. It automatically exports them to the Assets/Heightmap folder. Make sure all terrains between scenes have unique names if you want them to have different .raw exports.

```{r}
library(terra)
library(ggplot2)
library(tidyterra)

setwd(this.path::here("../..")) #Note - to get this to run, install the package 'this.path' from CRAN first. 

height.location = paste(getwd(), "/Heightmap/", sep="")

wh <- c(1025, 1025) #dimensions of the raw files
prod(wh) #this should match the raw file size

#this function imports the raw files and reverses their direction so they're read in the same order that ggplot will expect them in later.
import.raw <- function(x){
  raw.1 <- readBin(paste(height.location, x, sep = ""), "integer", n = prod(wh), size = 2, signed = TRUE, endian = "little")
  raw.2 <- t(matrix(data = raw.1, nrow = wh[1], ncol = wh[2])) #transpose and make matrix
  raw.3 <- apply(raw.2, 2, rev) #reverse vertical so it all meshes
  return(raw.3)
}

du <- import.raw("Dunes.raw")
ss  <- import.raw("Sandy_Shores.raw")
fo  <- import.raw("Forestlands.raw")

sh <- import.raw("Shrublands.raw")
ca <- import.raw("Cave_A.raw")
bp  <- import.raw("Bone_pile.raw")

is <- import.raw("Island.raw")
cb <- import.raw("Cave_B.raw")
gs <- import.raw("Grasslands.raw")


#This binds together the terrain into a single raster image
row1 <- do.call(cbind, list(du, ss, fo))
row2 <- do.call(cbind, list(sh, ca, bp))
row3 <- do.call(cbind, list(is, cb, gs))
together <- do.call(rbind, list(row1, row2, row3))
together.1 <- rast(together)
```



# The Modern Map
Because the modern map has no lake, it has a higher number of elevation breaks.
```{r}
mybreaks = c(-Inf, 330, seq(2000, 22000, by = 2000))

mycol = c("cadetblue", "#ffedd8", "#f3d5b5", "#e7bc91", "#bc8a5f", "#a47148", "#8b5e34", "#6f4518", "#414833", "#656d4a", "#a4ac86", "#a4ac86")

ggplot()+
  geom_spatraster_contour_filled(data=together.1, breaks = mybreaks) +
  scale_fill_manual(values = mycol)+
  theme_void() +
  theme(legend.position = "none")

ggsave("NewMapSystem/Modern_Map_Detailed_Update.png", dpi = 72, width = 1800, height = 1800, units = "px")
```


# The Pleistocene
Most of it is underwater so we make that the cadet blue color.
```{r}
mybreaks2 = c(-Inf, seq(4000, 22000, by = 2000))

mycol2 = c("cadetblue", "#ffedd8", "#f3d5b5", "#e7bc91", "#bc8a5f", "#a47148", "#414833", "#656d4a", "#a4ac86", "#a4ac86")

ggplot()+
  geom_spatraster_contour_filled(data=together.1, breaks = mybreaks2) +
  scale_fill_manual(values = mycol2)+
  theme_void() +
  theme(legend.position = "none")

ggsave("NewMapSystem/Pleistocene_Map_Detailed_Update.png", dpi = 72, width = 1800, height = 1800, units = "px")
```



# Resources Used

https://stackoverflow.com/questions/50361059/import-raw-image-in-r
https://forum.posit.co/t/solution-to-reading-raw-images-into-r/45435/8
https://dieghernan.github.io/tidyterra/reference/geom_spat_contour.html
https://rdrr.io/cran/raster/man/rasterToContour.html